---
title: "Shiny - Week 4 Assignment"
author: "Ganesh Prabhupatkar"
date: "June 24, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Developing Data Products using Shiny - Assignment Week 4

- Introduction
- A Shiny application was developed to predict mpg based on selected variable
- Application can be found in: https://gpatkar.shinyapps.io/shiny_assignment/
- The source code is provided on Github:https://github.com/ganeshppatkar/Shiny-App---Week-4.git
- A select box on the left side in the user interface can be used to select the variable for which the linear regression should be conducted.
- The outputs include the linear model for MPG agains selected variable.

## Data Used for the Regression Analyses
 
- Data Set - mtcars

## Linear Regressions Variables
- mpg (Miles/(US) gallon) is the predicted value and the predictors are:
- Number of Cylinders (cyl)
- horsepower (hp)
- Weight (wt)

## Linear Regressions
The following R code and plot the linear regression variable
```{r lm, echo = TRUE}
lm_f <- lm(mpg ~ wt, data = mtcars)
plot(mpg ~ wt, data = mtcars, ylab="MPG", xlab="Weight",col="blue")
abline(lm_f)
```



